---
title: "Cox_Model_example1"
author: "Rachel"
date: "5/18/2022"
output: github_document
---

#Two R packages: 1. 'survival' for computing survival analyses; 2. 'survminer' for visualizing survival analysis results 

#Load the packages 
```{r}
library("survival")
library("survminer")
```

#Example

##1. data: 
```{r}
data("lung")
head(lung)
```

##2. Compute the cox model: fit the Cox regression using covariates: age, sex, ph.ecog and wt.loss. 

    ##2.1 Univariate Cox regression: 
    
```{r}
res.cox = coxph(Surv(time, status) ~ sex, data = lung)
res.cox
```
    
```{r}
summary(res.cox)
```

##To apply the univariate coxph function to multiple covariates at once, type this:
```{r}
covariates = c("age", "sex", "ph.karno", "ph.ecog", "wt.loss")
univ_formulas = sapply(covariates, 
                       function(x) as.formula(paste('Surv(time, status)~', x)))

univ_models = lapply(univ_formulas, function(x){coxph(x, data = lung)})

#Extract data: 

univ_results = lapply(univ_models, function(x){
                                      x = summary(x)
                                      p.value = signif(x$wald["pvalue"], digits = 2)
                                      wald.test = signif(x$wald["test"], digits = 2)
                                      beta = signif(x$coef[1], digits = 2); #coeficient beta
                                      HR = signif(x$coef[2], digits = 2); #exp(beta)
                                      HR.confint.lower = signif(x$conf.int[, "lower .95"], 2)
                                      HR.confint.upper = signif(x$conf.int[, "upper .95"], 2)
                                      HR = paste0(HR, "(", 
                                                  HR.confint.lower, "-", HR.confint.upper,")")
                                      res = c(beta, HR, wald.test, p.value)
                                      names(res) = c("beta", "HR(95% CI for HR)", "wald.test", "p.value")
                                      return(res)
                                        ##returen(exp(cbind(coef(x), confint(X))))
})

res = t(as.data.frame(univ_results, check.names = FALSE))
as.data.frame(res)
```


##Multivariate Cox regression analysis 
```{r}
res.cox = coxph(Surv(time, status) ~ age + sex + ph.ecog, data = lung)
summary(res.cox)
```

##Visualizing the estimated distribution of survival times 
    #Plot the baseline survival function 
```{r}
ggsurvplot(survfit(res.cox), data = lung, palette = "#2E9FDF",
          ggtheme = theme_minimal())
```


#Create the new data
```{r}
sex_df = with(lung, data.frame(sex = c(1,2),
                               age = rep(mean(age, na.rm = TRUE), 2),
                               ph.ecog = c(1,1)
                               )
              )
sex_df

```

##Survival Curves
```{r}
fit = survfit(res.cox, newdata = sex_df)
ggsurvplot(data = lung, fit, conf.int = TRUE, legend.labs = c("Sex = 1", "Sex = 2"),
           ggtheme = theme_minimal())
```




